### 2012-12-19 Docs/managing_jobs/managingjobs.tex
some hopper notes

\section{Automatic Restarting and Archiving of Data}

@@

\section{Remote \visit\ Visualization on Lens}

@@

>>>>

\section{Working at OLCF (ORNL)}

\subsection{Automatic Restarting and Archiving of Data}

@@

\subsection{Remote \visit\ Visualization on Lens}

@@

\section{Working at NERSC}

\subsection{Using the {\tt AmrPostprocesing} python plotting scripts on hopper}

To build the {\tt fsnapshot.so} library, you need to do:
\begin{verbatim}
module load gcc
\end{verbatim}
{\tt f2py} is already in the path, so the library should then build without issue.
%

Then edit your {\tt .bashrc.ext} file to set the {\tt PYTHONPATH} to
the {\tt python\_plotfile} directory, e.g.:
\begin{verbatim}
export PYTHONPATH="/global/homes/z/zingale/AmrPostprocessing/F\_Src/python_plotfile"
\end{verbatim}
%
and set the {\tt PATH} to that directory,
\begin{verbatim}
export PATH="/global/homes/z/zingale/AmrPostprocessing/F_Src/python_plotfile:$PATH"
\end{verbatim}

To run the script, you need to do:
\begin{verbatim}
module load matplotlib
module load python
\end{verbatim}

\subsection{Remote visualization on hopper}

\visit\ is already configured to work with hopper.  If the host does not appear
in your local version of visit, copy the {\tt host\_nersc\_hopper.xml} file
from the {\tt .visit/allhosts/} directory under the system's \visit\ install path
to your {\tt $\mathtt{\sim}$/.visit/hosts/} directory.
